BERT Model Compression and Weight Sharing

### 2019-05-13 paper/paper.tex
Write draft of conclusion section

% TODO: talk about bringing in outside data for KD

\begin{itemize}
\item What happened?
\item What next?
\end{itemize}

% \section*{Acknowledgements}

>>>>

Knowledge Distillation displayed promise by improving student networks'
performance versus training only on the classes $y_i$. However, the student
networks fell short of replicating uncompressed BERT's performance. It is
possible that future variations on our work could achieve competitive
compression. In particular, we restrict our knowledge distillation only to the
samples in the original training set. However, there is no need to perform
training so narrowly since the teacher network can annotate any unsupervised
data. It is likely that doing so would further increase performance, though we
can only speculate as to the magnitude of the benefit.

It is also possible that our choice of student network colored our results. We
aimed for architectures known to work on SST-2 while being much smaller, such as
\citet{kim2014convolutional}'s CNN. It is possible that we aimed too small and
would be better served by a more complex model---possibly even a smaller version
of BERT. Finally, in all our experiments our teacher network is a single
fine-tuned version of BERT. Since teacher network complexity doesn't contribute
to the complexity of the final model, we could instead use an ensemble of BERTs
(or even other models) as our teacher network.

The DeepTwist framework---particularly when combined with difference
pruning---exceeded our expectations for compression. It would be interesting to
test whether this generalizes to a wider array of tasks, particularly since we
only reap compression benefits as we leverage weight sharing over a number of
tasks. Furthermore, from the distortions presented in \citet{lee2018deeptwist},
we did not implement clustering-based quantization because of the significant
computational bottleneck clustering with $k$-means on all of BERT's parameters
posed. Future work could attempt to surmount this obstacle whether through
increased computational resources or a more scalable clustering algorithm.

Finally, we recognize our approaches are but a subset of the ways to go about
compressing large language models such as BERT. Two alternatives stand out as
particularly exciting possible future directions. \citet{liu2019multi} propose a
method for complete weight sharing of BERT's encoder parameters across different
tasks by simultaneously training for all tasks. We believe this approach could
be relaxed through difference pruning to achieve a performance gain relative to
each compression technique in isolation.

% TODO: reverse of deeptwist -- what paper was this?

\section*{Acknowledgements}

% TODO: thank Rush + 287
